Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-16 Paperfolder/Paperfolder.Rmd
Updated according to hy comments v0_0_1

#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.

@@

  The aim was to further examine the relationship between milk intake and stroke mortality among the Japanese population. We used data from the Japan Collaborative Cohort Study to estimate the posterior acceleration factors (AF) as well as the hazard ratios (HR) comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline. These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process. 100000 posterior samples for each individual were generated separately through four independent chains after model convergency were confirmed. Posterior probabilites that daily milk consumers had lower hazard or delayed mortality from strokes compared to non-consumers was 99.0% and 78.0% for men and women, respectively. Accordingly, the estimated posterior means of AF and HR for daily milk consumers were 0.88 (95% Credible Interval, CrI: 0.81, 0.96) and 0.80 (95% CrI: 0.69, 0.93) for men and 0.97 (95% CrI: 0.88, 1.10) and 0.95 (95% CrI: 0.80, 1.17) for women.

@@

Dairy food, especially milk has been recommended to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016]. More intuitive interpretation for a decreasing risk would be possible if we were able to compute the exact probability for people who had milk intake may had lower hazard of dying from stroke compared with those who never drank milk at all. For general public/media reporting, concept of hazard in epidemiological studies could still sometimes be challenging to be understood or misinterpreted since hazard is formally defined as the probability of the occurrence of an event at a given time point [@collett2015modelling]. Usually, authors of epidemiological papers would tend to use "risk" instead of "hazard" or interchangeably. However, it would still possibly be mixed up with "risk" that only contain pure meaning of "probability of an event" without redefining a point or a period of time in cross-sectional settings. For better understanding and interpretation of the findings from data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other. Another approach of comparing the time-to-event survival probabilities between different groups would be to model the time before observing an event rather than the hazard which always required the assumption of a proportional hazard to be met. Accelerated failure time models are among these convenient tools that would avoid worrying about the assumption of proportional hazard and directly showing how faster/slower one individual in an exposure group might have an event compared to others among different exposure groups [@Wei1992].

Our aim was to overcome these potential pitfalls, avoid misunderstanding, and provide a more straightforward answer to the main research question that whether someone answered he/she drank milk at the baseline of study had lower hazard of dying from stroke compared with his/her counterparts who said they never consumed milk. If the answer to the primary objective was yes, then the probabilities that individuals with different frequencies of milk intake may had lower hazard compared with those who never drank milk were calculated through a Markov Chain Monte Carlo (MCMC) simulation process. A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay or slow down the speed towards a mortality from stroke event from happening after controlling for the other potential confounders.

@@

We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake. Overall difference across the milk intake groups were tested by either analysis of variance for continuous variables or $\chi^2$ test for categorical variables.

@@

The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women). Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women).

@@

<!-- - strength and limitation of current study -->
Some limitations here are worth mentioning. First, although our object was not to answer which type of milk is protective, but if such information were somehow available in the JACC study database, more detailed comparison or stratification would have been possible. Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable. Therefore, we did not try to compute the amount of consumption by multiplying an average volume per occasion with the frequency of intake since the random error might be exaggerated and the observed associations may have attenuated. Strengths of our analyses included that we have transformed the research questions to more transparent ones that is easier for interpretation. Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulation.

>>>>

@@

  The aim was to further examine the relationship between milk intake and stroke mortality among the Japanese population. We used data from the Japan Collaborative Cohort (JACC) Study to estimate the posterior acceleration factors (AF) as well as the hazard ratios (HR) comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline. These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process. 100000 posterior samples for each individual were generated separately through four independent chains after model convergency were confirmed. Posterior probabilites that daily milk consumers had lower hazard or delayed mortality from strokes compared to non-consumers was 99.0% and 78.0% for men and women, respectively. Accordingly, the estimated posterior means of AF and HR for daily milk consumers were 0.88 (95% Credible Interval, CrI: 0.81, 0.96) and 0.80 (95% CrI: 0.69, 0.93) for men and 0.97 (95% CrI: 0.88, 1.10) and 0.95 (95% CrI: 0.80, 1.17) for women. In conclusion, data from the JACC study has provided strong evidence that daily milk intake among Japanese men was associated with delayed and lower hazard of mortality from stroke especially cerebral infarction.

@@

Eastern Asian populations were reported to have higher burden from either mortality or morbidity from stroke than populations in European or American regions [@Kim2014]. Dairy food, especially milk has been suggested to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016]. Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in the Western countries [@Saito2019]. Given that previous reports have also indicated no significant [@Iso1999;@sauvaget2003intake;@Elwood2004] or even positive associations [@Larsson2009], whether people with such a low level intake of milk can still benefit against stroke would be questionable. Even if there is any benefit, not every individual with habitual milk intake can avoid dying from stroke. A more intuitive interpretation would be available if we were able to show the probabilities and how certain the existing data can provide evidence about whether drinking milk can delay a stroke event or lower the hazard of dying from stroke. Accelerated failure time models under Bayesian framework are convenient tools that would help avoid worrying about the assumption of proportional hazard normally required in a Cox proportional hazard model and can directly show how faster/slower individuals in an exposure group might have an event compared to others among different exposure groups [@Wei1992;@ibrahim2014b].

Our aim was to provide a more straightforward answer to the primary research question that whether someone answered he/she drank milk at the baseline of study had lower hazard of dying from stroke compared with his/her counterparts who said they never consumed milk. If the answer to the primary objective was yes, then the probabilities that individuals with different frequencies of milk intake may had lower hazard compared with those who never drank milk were calculated through a Markov Chain Monte Carlo (MCMC) simulation process. A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay a stroke mortality event from happening after controlling for the other potential confounders.

@@

We calculated sex-specific means (standard deviation, sd) and proportion of selected baseline characteristics according to the frequency of milk intake. Age-adjusted stroke mortality rate were expressed as per 1000 person-year through the poisson regression model.

@@

The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women). Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women). Age-adjusted stroke mortality rate for each category of milk intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for women.

@@

<!-- - strength and limitation of current study -->
Some limitations here are worth mentioning. First, the milk intake frequency as well as other lifestyle information was collected only once at the baseline and was self-reported. Apparently habits in life are possible to alter over the time and these would resulted in misclassfication and residual confoudings. Second, despite reasonable validity of FFQ in the JACC study cohort was assessed and confirmed, measurement errors are inevitable. Therefore, we did not try to compute the amount of consumption by multiplying an average volume per occasion with the frequency of intake since the random error might be exaggerated and the observed associations may have attenuated. Strengths of our analyses included that we have transformed the research questions to more transparent ones that is easier for interpretation. Direct probabilities that daily milk intake is associated with lower hazard or delayed stroke mortality event were provided here after thorough computer simulation.

### 2020-07-16 Paperfolder/Paperfolder.tex
Updated according to hy comments v0_0_1

%=================================================================
\documentclass[nutrients,article,To be
submitted,moreauthors,pdftex]{mdpi}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{The aim was to further examine the relationship between milk
intake and stroke mortality among the Japanese population. We used data
from the Japan Collaborative Cohort Study to estimate the posterior
acceleration factors (AF) as well as the hazard ratios (HR) comparing
individuals with different milk intake frequencies against those who
never consumed milk at the study baseline. These estimations were
computed through a series of Bayesian survival models that employed a
Markov Chain Monte Carlo simulation process. 100000 posterior samples
for each individual were generated separately through four independent
chains after model convergency were confirmed. Posterior probabilites
that daily milk consumers had lower hazard or delayed mortality from
strokes compared to non-consumers was 99.0\% and 78.0\% for men and
women, respectively. Accordingly, the estimated posterior means of AF
and HR for daily milk consumers were 0.88 (95\% Credible Interval, CrI:
0.81, 0.96) and 0.80 (95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI:
0.88, 1.10) and 0.95 (95\% CrI: 0.80, 1.17) for women.}

@@

Dairy food, especially milk has been recommended to reduce stroke risk
by nearly 7\% for each 200 g increment of daily consumption
\citep{DeGoede2016}. More intuitive interpretation for a decreasing risk
would be possible if we were able to compute the exact probability for
people who had milk intake may had lower hazard of dying from stroke
compared with those who never drank milk at all. For general
public/media reporting, concept of hazard in epidemiological studies
could still sometimes be challenging to be understood or misinterpreted
since hazard is formally defined as the probability of the occurrence of
an event at a given time point \citep{collett2015modelling}. Usually,
authors of epidemiological papers would tend to use ``risk'' instead of
``hazard'' or interchangeably. However, it would still possibly be mixed
up with ``risk'' that only contain pure meaning of ``probability of an
event'' without redefining a point or a period of time in
cross-sectional settings. For better understanding and interpretation of
the findings from data that researchers endeavored to collect,
statistical literature have provided plenty of choices that could help
us better communicate with each other. Another approach of comparing the
time-to-event survival probabilities between different groups would be
to model the time before observing an event rather than the hazard which
always required the assumption of a proportional hazard to be met.
Accelerated failure time models are among these convenient tools that
would avoid worrying about the assumption of proportional hazard and
directly showing how faster/slower one individual in an exposure group
might have an event compared to others among different exposure groups
\citep{Wei1992}.

Our aim was to overcome these potential pitfalls, avoid
misunderstanding, and provide a more straightforward answer to the main
research question that whether someone answered he/she drank milk at the
baseline of study had lower hazard of dying from stroke compared with
his/her counterparts who said they never consumed milk. If the answer to
the primary objective was yes, then the probabilities that individuals
with different frequencies of milk intake may had lower hazard compared
with those who never drank milk were calculated through a Markov Chain
Monte Carlo (MCMC) simulation process. A Bayesian survival analysis
method was applied on an existing database and through which, we also
provided estimates about whether drinking milk could delay or slow down
the speed towards a mortality from stroke event from happening after
controlling for the other potential confounders.

@@

We calculated sex-specific means (standard deviation, sd) and proportion
of selected baseline characteristics according to the frequency of milk
intake. Overall difference across the milk intake groups were tested by
either analysis of variance for continuous variables or \(\chi^2\) test
for categorical variables.

@@

Some limitations here are worth mentioning. First, although our object
was not to answer which type of milk is protective, but if such
information were somehow available in the JACC study database, more
detailed comparison or stratification would have been possible. Second,
despite reasonable validity of FFQ in the JACC study cohort was assessed
and confirmed, measurement errors are inevitable. Therefore, we did not
try to compute the amount of consumption by multiplying an average
volume per occasion with the frequency of intake since the random error
might be exaggerated and the observed associations may have attenuated.
Strengths of our analyses included that we have transformed the research
questions to more transparent ones that is easier for interpretation.
Direct probabilities that daily milk intake is associated with lower
hazard or delayed stroke mortality event were provided here after
thorough computer simulation.

>>>>

%=================================================================
\documentclass[nutrients,article,submitted,moreauthors,pdftex]{mdpi}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{The aim was to further examine the relationship between milk
intake and stroke mortality among the Japanese population. We used data
from the Japan Collaborative Cohort (JACC) Study to estimate the
posterior acceleration factors (AF) as well as the hazard ratios (HR)
comparing individuals with different milk intake frequencies against
those who never consumed milk at the study baseline. These estimations
were computed through a series of Bayesian survival models that employed
a Markov Chain Monte Carlo simulation process. 100000 posterior samples
for each individual were generated separately through four independent
chains after model convergency were confirmed. Posterior probabilites
that daily milk consumers had lower hazard or delayed mortality from
strokes compared to non-consumers was 99.0\% and 78.0\% for men and
women, respectively. Accordingly, the estimated posterior means of AF
and HR for daily milk consumers were 0.88 (95\% Credible Interval, CrI:
0.81, 0.96) and 0.80 (95\% CrI: 0.69, 0.93) for men and 0.97 (95\% CrI:
0.88, 1.10) and 0.95 (95\% CrI: 0.80, 1.17) for women. In conclusion,
data from the JACC study has provided strong evidence that daily milk
intake among Japanese men was associated with delayed and lower hazard
of mortality from stroke especially cerebral infarction.}

@@

Eastern Asian populations were reported to have higher burden from
either mortality or morbidity from stroke than populations in European
or American regions \citep{Kim2014}. Dairy food, especially milk has
been suggested to reduce stroke risk by nearly 7\% for each 200 g
increment of daily consumption \citep{DeGoede2016}. Although 2 daily
servings of milk or dairy products is recommended in Japan
\citep{Yoshiike2007}, the actual per capita intake (\(\approx\) 63
g/day) of these food groups is much lower and less frequent than that in
the Western countries \citep{Saito2019}. Given that previous reports
have also indicated no significant
\citep{Iso1999, sauvaget2003intake, Elwood2004} or even positive
associations \citep{Larsson2009}, whether people with such a low level
intake of milk can still benefit against stroke would be questionable.
Even if there is any benefit, not every individual with habitual milk
intake can avoid dying from stroke. A more intuitive interpretation
would be available if we were able to show the probabilities and how
certain the existing data can provide evidence about whether drinking
milk can delay a stroke event or lower the hazard of dying from stroke.
Accelerated failure time models under Bayesian framework are convenient
tools that would help avoid worrying about the assumption of
proportional hazard normally required in a Cox proportional hazard model
and can directly show how faster/slower individuals in an exposure group
might have an event compared to others among different exposure groups
\citep{Wei1992, ibrahim2014b}.

Our aim was to provide a more straightforward answer to the primary
research question that whether someone answered he/she drank milk at the
baseline of study had lower hazard of dying from stroke compared with
his/her counterparts who said they never consumed milk. If the answer to
the primary objective was yes, then the probabilities that individuals
with different frequencies of milk intake may had lower hazard compared
with those who never drank milk were calculated through a Markov Chain
Monte Carlo (MCMC) simulation process. A Bayesian survival analysis
method was applied on an existing database and through which, we also
provided estimates about whether drinking milk could delay a stroke
mortality event from happening after controlling for the other potential
confounders.

@@

We calculated sex-specific means (standard deviation, sd) and proportion
of selected baseline characteristics according to the frequency of milk
intake. Age-adjusted stroke mortality rate were expressed as per 1000
person-year through the poisson regression model.

@@

Some limitations here are worth mentioning. First, the milk intake
frequency as well as other lifestyle information was collected only once
at the baseline and was self-reported. Apparently habits in life are
possible to alter over the time and these would resulted in
misclassfication and residual confoudings. Second, despite reasonable
validity of FFQ in the JACC study cohort was assessed and confirmed,
measurement errors are inevitable. Therefore, we did not try to compute
the amount of consumption by multiplying an average volume per occasion
with the frequency of intake since the random error might be exaggerated
and the observed associations may have attenuated. Strengths of our
analyses included that we have transformed the research questions to
more transparent ones that is easier for interpretation. Direct
probabilities that daily milk intake is associated with lower hazard or
delayed stroke mortality event were provided here after thorough
computer simulation.
